Title

### 2012-06-22 inc/magnetic_lenses/maglens.tex

To further ease the burden on the lenses, I actually created two, one placed to either side of the RF cavity.
As each has 100 turns, a current of only 2A is needed to drive the two lenses in series.
The oxygen-free copper wire coils remain cool to the touch under these operating conditions.

>>>>

To manage the divergence created by an RF cavity, two lenses are employed (one before and one after the cavity), forming a lens system of a similar effective focal length.
For the purposes of design, one can make a reasonable approximation that the two lenses together may together provide the total number of needed amp-turns.
As each has 100 turns, a current of only about 2A is needed to drive the two lenses in series.

\subsection{Thermal Properties}

%TODO need reference for equation and \alpha_{Cu}
Since the lenses have no cooling devices, it was prudent to characterize the thermal response to a moderate current load.
Resistance of metals changes as a function of temperature by $ R = R_0 [ 1 + \alpha ( T - T_0 ) ] $, where $\alpha$ is a material contant; for copper, $\alpha = 3.9 * 10^{-3} \text{K}^{-1}$. 
One can calculate the temperature increase of the system by monitoring the change in resistance.
Maintaining a constant current of 4A through the lens, the voltage drop increased from 1.22V ($R_0 = 0.305\Omega$) to 1.25V ($R=0.3125\Omega$) as the lens warmed.
The resultant temperature increase is only $T - T_0 = 2\text{K}$.
This result is easily confirmed manually; the oxygen-free copper wire coils remain cool to the touch under these operating conditions.
